Generality in food webs scales with species richness, not latitude

### 2014-07-24 manuscript/latitudepaper.tex
Starting to change things.

%Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
Food webs (networks of feeding links between species) have been used for decades to summarize the structure of 
ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, temperature?, latitude?. 
Latitude is of particular interest as an environmental driver of food-web structure because it entails gradients in 
temperature \citep{}, primary productivity \citep{}, and seasonality \citep{}. Indeed, each of these latitudinal 
environmental gradients has been put forward as a driver for the latitudinal gradient in species richness, one of
the most general and robust patterns in ecology \citep{Schemske2009a,,}.

This effect of latitude on species richness, however, presents a problem for the analysis of other aspects of food-web structure.
Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
analyses with higher-quality data have revealed that most food-web structural properties scale strongly with species 
richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that relationships
between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
This is especially true for food-web properties that both scale with species richness and are related to candidate
explanations for the latitudinal diversity gradient, such as measures of specialization.

% Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
%Then give hypotheses.
A latitudinal gradient in specialization lies behind the ``latitude-niche breadth hypothesis'' \citep{Vazquez2004}.
This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
coexist in the tropics than can at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocably 
supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.

Importantly, the expectation of the latitude-niche breadth hypothesis that higher species richness is associated with 
reduced competition is contary to the expected increase in the mean number of interactions per species (one potential 
measure of specialization) as species richness increases \citep{Dunne2006,Riede2010}. If, therefore, there is a
distinct effect of latitude on specialization then this effect should be visible in changing scaling relationships.
Here, we tested the effect of latitude on scaling relationships between species richness and mean links per species, 
mean generality (number of prey per predator), and mean vulnerability (number of predators per prey). Together, these
properties provide a measure a species' biotic specialization - that is, its specialization in terms of interactions 
with other species.

>>>>

%Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
Food webs --networks of feeding links between species-- have been used for over a century to summarize the structure of 
ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and temperature. The latter
variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics \citep{}, 
suggesting that latitude may indirectly affect food-web structure.
Indeed, these latitudinal environmental gradients have been put forward as potential driverd for the latitudinal gradient in species 
richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.

This effect of latitude on species richness, however, presents a problem for the analysis of other aspects of food-web structure.
Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
analyses with higher-quality data have revealed that most food-web structural properties scale strongly with species 
richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that any relationship
between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
This is especially true for food-web properties that both scale with species richness and are related to candidate
explanations for the latitudinal diversity gradient, such as measures of specialization [[DBS requests citation, ARC thinks this is the motivation for the paper and isn't aware of a source]].

[[Smoother transition needed here]]
% Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
%Then give hypotheses.
A latitudinal gradient in specialization lies behind the ``latitude-niche breadth hypothesis'' \citep{Vazquez2004}.
This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
coexist in the tropics than can at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocably 
supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.

Importantly, the expectation of the latitude-niche breadth hypothesis that higher species richness is associated with 
reduced competition is contary to the expected increase in the mean number of interactions per species (one potential 
measure of specialization) as species richness increases \citep{Dunne2006,Riede2010}. If, therefore, there is a
distinct effect of latitude on specialization then this effect should be visible in changing scaling relationships.
Here, we tested for changes in the scaling of mean links per species, mean generality, and mean vulnerability with species
richness over latitude. We focused on these three food-web properties --only some of the wide array of metrics that have been
described (see e.g. \citep{})-- because together they provide a measure a species' biotic specialization, which underlies the 
``latitude-niche breadth hypothesis''.
